paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

# Model Summaries (Note coefficients are per 1000 women)
table_5 <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = all_state_model_no_dist$coefficients[2]*1000,
                  "p-value" = c('< 0.001')) %>% 
  kbl(caption = "All States Data: Change in Abortions per 1000 Women in Model without Distances", 
          digits = 3) %>%
  kable_styling(latex_options = 'hold_position')
table_5

p <- all_state_model_dist$coefficients[4,4] %>% round(3)
table_6 <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(all_state_model_dist$coefficients[2]*1000, 
                           all_state_model_dist$coefficients[3]*1000,
                           all_state_model_dist$coefficients[4]*1000),
                  "p-value" = c('< 0.001', '< 0.001', p)) %>%
  kbl(caption = "All States Data: Change in Abortions per 1000 Women in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_6

>>>>

# Model Summaries (Note coefficients are per 1000 women)
# Model Summaries (Note coefficients are per 1000 women)
table_5 <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = all_state_model_no_dist$coefficients[2]*1000,
                  "95% CI lower" = all_state_model_no_dist$coefficients[2,1]*1000-all_state_model_no_dist$coefficients[2,2]*1000*1.96,
                  "95% CI upper" = all_state_model_no_dist$coefficients[2,1]*1000+all_state_model_no_dist$coefficients[2,2]*1000*1.96,
                  "p-value" = c('< 0.001')
                  ) %>% 
  kbl(caption = "All States Data: Change in Abortions per 1000 Women in Model without Distances", 
          digits = 3) %>%
  kable_styling(latex_options = 'hold_position')
table_5

p <- all_state_model_dist$coefficients[4,4] %>% round(3)
table_6 <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(all_state_model_dist$coefficients[2]*1000, 
                           all_state_model_dist$coefficients[3]*1000,
                           all_state_model_dist$coefficients[4]*1000),
                  "95% CI lower" = c(all_state_model_dist$coefficients[2,1]*1000-all_state_model_dist$coefficients[2,2]*1000*1.96,
                                     all_state_model_dist$coefficients[3,1]*1000-all_state_model_dist$coefficients[3,2]*1000*1.96,
                                     all_state_model_dist$coefficients[4,1]*1000-all_state_model_dist$coefficients[4,2]*1000*1.96),
                  "95% CI upper" = c(all_state_model_dist$coefficients[2,1]*1000+all_state_model_dist$coefficients[2,2]*1000*1.96,
                                     all_state_model_dist$coefficients[3,1]*1000+all_state_model_dist$coefficients[3,2]*1000*1.96,
                                     all_state_model_dist$coefficients[4,1]*1000+all_state_model_dist$coefficients[4,2]*1000*1.96),
                  "p-value" = c('< 0.001', '< 0.001', p)) %>%
  kbl(caption = "All States Data: Change in Abortions per 1000 Women in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_6
